Is it time for an NBA expansion?

### 2024-04-15 paper/paper.qmd
Model update

library(tidyverse)
library(readr)
library(modelsummary)

@@

# Simulating data
set.seed(123)  # For reproducibility
sim_nba_data <- data.frame(
  Year = rep(1980:2023, times = 10),  # Simulate 10 records per year
  Num_teams = c(rep(22, each = 1 * 10),
                rep(23, each = 8 * 10),
                rep(25, each = 1 * 10),
                rep(27, each = 6 * 10),
                rep(29, each = 9 * 10),
                rep(30, each = 19 * 10)),  # Adjusted each parameter as needed
  PTS = rnorm(440, mean = mean(full_nba_data$PTS), sd = sd(full_nba_data$PTS)),  
  AST = rnorm(440, mean = mean(full_nba_data$AST), sd = sd(full_nba_data$AST)), 
  TRB = rnorm(440, mean = mean(full_nba_data$TRB), sd = sd(full_nba_data$TRB)),  
  STL = rnorm(440, mean = mean(full_nba_data$STL), sd = sd(full_nba_data$STL)),  
  BLK = rnorm(440, mean = mean(full_nba_data$BLK), sd = sd(full_nba_data$BLK)),  
  TOV = rnorm(440, mean = mean(full_nba_data$TOV), sd = sd(full_nba_data$TOV)) 
)
# Add a column for PPG that depends on the year and number of teams, 
# as well as other factors. Adjust the coefficients as needed for your simulation.
sim_nba_data_1 <- sim_nba_data %>%
  mutate(PPG = (PTS / 82) + (Year - 1980) * 0.2 - (Num_teams - 22) * 0.1 +
                0.1 * AST + 0.05 * TRB - 0.05 * STL + 0.05 * BLK - 0.05 * TOV)

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
nba_model_1 <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data_1)

# Summary of the linear model
msummary(nba_model)
modelsummary(nba_model_1)

@@

exp_year <- c(1988, 1989, 1995, 2004) #Exansion Year

>>>>

library(tidyverse)
library(readr)
library(modelsummary)
library(tinytex)
```

@@

# Simulating data
set.seed(123)  # For reproducibility
sim_nba_data <- data.frame(
  Year = rep(1980:2023, times = 10),  # Simulate 10 records per year
  Num_teams = c(rep(22, each = 1 * 10),
                rep(23, each = 8 * 10),
                rep(25, each = 1 * 10),
                rep(27, each = 6 * 10),
                rep(29, each = 9 * 10),
                rep(30, each = 19 * 10)),  # Adjusted each parameter as needed
  PTS = rnorm(440, mean = mean(full_nba_data$PTS), sd = sd(full_nba_data$PTS)),  
  AST = rnorm(440, mean = mean(full_nba_data$AST), sd = sd(full_nba_data$AST)), 
  TRB = rnorm(440, mean = mean(full_nba_data$TRB), sd = sd(full_nba_data$TRB)),  
  STL = rnorm(440, mean = mean(full_nba_data$STL), sd = sd(full_nba_data$STL)),  
  BLK = rnorm(440, mean = mean(full_nba_data$BLK), sd = sd(full_nba_data$BLK)),  
  TOV = rnorm(440, mean = mean(full_nba_data$TOV), sd = sd(full_nba_data$TOV)) 
)

# Fit a multiple linear regression model
nba_model <- lm(PTS ~ Year * Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)
madal <- lm(PTS ~ Year + Num_teams + AST + TRB + STL + BLK + TOV, data = sim_nba_data)

# Summary of the linear model
msummary(
  list(
    "times" = nba_model,
    "plus" = madal
  ),
  fmt = 2
  )

@@

exp_year <- c(1988, 1989, 1995, 2004) #Expansion Year
